Cryptographic assurance of secrecy and fairness in voting

### 2012-12-08 paper/paper.tex
Fix repetition of "actually"
pret-a vis-a-vis coercion resistance

>>>>

\term{\pv{}} acknowledges that it generally only provides receipt-freeness and thus voter privacy, but fails to
truly resist coercion. It offers receipt-freeness, despite providing voters with a receipt, because a voter
cannot use her receipt to prove for whom she voted. Absent perfect physical security, though, coercion may still be possible
by, for example, sneaking complete, blank ballot forms out of the polling place, recording the candidate list ordering and onion on each,
giving the forms to other voters to sneak in and use to vote, and then requiring those voters to show that their signed receipt, matched with the now-known candidate ordering, indicates they voted as instructed.
